### 2018-07-13 submission/manuscript.Rmd
fix intro with lab suggestions

**Conclusions.** Although there are 16S rRNA gene sequencing differences based on polymerase and number of cycles used, they are small with respect to the biological differences between fecal bacterial communities within indivdiuals. Collectively, these results provide evidence that a real biological difference between groups, based on 16S rRNA gene sequencing of fecal samples, should be detectable regardless of polymerase and number of cycles used.

@@

The bacterial community is reported to vary between case and control for a number of diseases [@Turnbaugh2008; @Baxter2016; @Sze2015; @Bonfili2017]. However, for diseases like obesity, the taxa identified have varied widely depending on the study [@Turnbaugh2008; @Zupancic2012]. Some of this variation could be due to error introduced during the 16S rRNA gene sequencing workflow. A typical 16S rRNA gene sequencing workflow can be divided into preservation, extraction, PCR, and sequencing steps. The preservation and extraction stages of the 16S rRNA gene sequencing workflow have been the most extensively studied [@contamination_Salter2014; @preservation_Song_2016; @storage_Bassis_2017; @review_Kim_2017]. For preservation and extraction stages of the workflow, it has been consistently found that there are errors in the observed bacterial community composition based on the kits used, but that these differences are smaller than the overall biological difference measured between samples with different kits [@preservation_Song_2016; @storage_Bassis_2017]. Since these studies use the same PCR approach while varying preservation or extraction method, the contribution of PCR error to this overall workflow is not well characterized.

There is a large body of literature that shows there are errors due to primer and number of cycles chosen for the PCR stage of 16S rRNA gene sequencing [@Eckert1991; @Burkardt2000]. Primers have variable region dependent binding affinities which causes an inability to detect specific bacteria (e.g. V1-V3 does not detect *Haemophilus influenzae* and V3-V5 does not detect *Propionibacterium acnes*) [@Meisel2016; @Sze2015 (Table S4)]. Another source of error is the selective amplification of AT-rich over GC-rich sequences which exaggerate the difference between 16S rRNA genes higher in AT versus those higher in GC content [@polz_bias_1998]. Many of these sources of error are made worse as the number of cycles increases [@Wang1996; @Haas2011; @Kebschull2015]. For example, both amplification error and non-specific amplification (e.g. incorrect amplicon size products) also can increase as the number of cycles increases. This will increase the number of Operational Taxonomic Units (OTUs) observed and drastically change the values obtained from commonly used diversity measures [@BautistadelosSantos2016; @Acinas2005]. Additionally, as the number of cycles increases more chimeras can form from an aborted extension step that causes a priming error and subsequent secondary extension [@Haas2011]. These chimeras will artificially increase community diversity by increasing the number of OTUs that are observed [@Haas2011]. In addition to these sources of errors, there also are multiple families of DNA polymerases that have their own error rate and proof reading capacity [@polymerase_Ishino_2014]. Interestingly, the influence that these different DNA polymerases can have on the observed 16S rRNA gene sequencing results have not been well studied like some of the other sources of PCR-based error

A recent study found differences in the number of OTUS and chimeras between normal and high fidelity DNA polymerases [@taq_Gohl_2016]. The authors of this study could reduce the difference between two polymerases by optimizing the annealing and extension steps within the PCR protocol [@taq_Gohl_2016]. Yet, within this study there was no comparison made between different high fidelity DNA polymerases on the same samples. Additionally, the fecal samples that were analyzed, as a model of a more complex community, had different processing methodolgies applied to the two different treatment groups tested, which could exagerate the observed biological differences. Due to these gaps, it is natural to extend the previous line of inquiry to include a more detailed examination of two specific areas. First, for the investigation of whether differences in PCR error are detected between high fidelity polymerases and number of cycles used. Second, for examining whether these differences in error are enough to obscure smaller biological signals than what has been previously reported [@taq_Gohl_2016]. Thus, this study will investigate whether differences in high fidelity DNA polymerases are due to error and whether these differences obscure the biological variation in the fecal bacterial community composition between individuals. We accomplish this by examining GC-based amplification error, sequence error (e.g. subsitutions), chimera prevalence, the number of OTUs, Bray-Curtis index, and OTU-based differences at varying number of cycles in five different high fidelity DNA polymerases. Additionally, we also created Random Forest models to classify number of cycles, polymerase, and individuals to assess which model had the best classification success when using 16S rRNA gene sequencing data.

@@

***Sequence processing.***
The mothur software program was used for all sequence processing steps [@mothur_schloss_2009]. The protocol has been previously published [@protocol_Kozich_2013] (https://www.mothur.org/wiki/MiSeq_SOP). Two major differences from the published protocol were the use of VSEARCH instead of UCHIME for chimera detection and the use of the OptiClust algorithm instead of average neighbor for OTU generation at 97% similarity [@vsearch_Rognes_2016; @uchime_Edgar_2011; @opticlust_Westcott_2017]. Sequence error was determined using the 'seq.error' command on mock samples to compare back to the reference 16S sequences of *P. aeruginosa*, *E. coli*, *S. enterica*, *L. fermentum*, *E. faecalis*, *S. aureus*, *L. monocytogenes*, and *B. subtilis* [@mothur_schloss_2009; @vsearch_Rognes_2016; @rdp_Cole_2013]. For simplicity, the use of the term 'error' within the context of this study moving forward encompasses changes in the downstream sequencing results due to the amplification step (e.g. higher GC content genomes, base subsitutions, deletions, insertions, non-specific amplification, chimeras, etc.).

@@

***Statistical analysis.***
All analysis was done with the R (v `r paste(version$major, ".", version$minor, sep = "")`) software package [@r_citation_2017]. Data transformation and graphing was completed using the tidyverse package (v `r paste(packageVersion("tidyverse")[1])`) and colors selected using the viridis package (v `r paste(packageVersion("viridis")[1])`) [@tidyverse_2017; @viridis_citation_2017]. High and low GC content was determined based on the median GC percentage of either the V4 region or the whole genome of the bacterial species used in the mock community. Differences in the total number of OTUs were analyzed using an ANOVA with a tukey post-hoc test. For the comparison of the number of OTUS in fecal samples the data was normalized to each individual by cycle number to account for the biological variation. Bray-Curtis distance matrices were generated using mothur. The distance matrix data was analyzed using PERMANOVA with the vegan package (v `r paste(packageVersion("vegan")[1])`) [@vegan_citation] and Kruskal-Wallis tests within R. The Random Forest models were run using the caret package (v `r paste(packageVersion("caret")[1])`) [@caret_citation]. A total of 100 10-fold CV runs on different 80/20 splits of the data was run to generate a range of the Logloss value. The probability of a correct call was obtained from this Logloss value by taking the negative natural logrithim. For both error and chimera analysis, samples were tested using Kruskal-Wallis with a Dunns post-hoc test. Where applicable, correction for multiple comparison utilized the Benjamini-Hochberg method [@benjamini_controlling_1995].

@@

***The number of OTUs generated are dependent on polymerase used.***
In addition to the sequence error and chimera differences between polymerases, we also investigated whether there were polymerase or number of cycle dependent effects on the observed number of OTUs. There was a polymerase dependent difference in the range of the number of OTUs in the mock community samples [Figure 3A]. The closest any of the polymerases came to a total of `r pull(ref_mock_otu_num, numOtus)` OTUs, created by running the mock reference 16S sequences through mothur processing, was at 25 and 30 cycles [Figure 3A]. Differences between polymerases for the number of OTUs created were observed as early as 20 cycles in the mock community (F-stat = `r round(filter(mock_anova_summary, sub_sample_level == 1000, cycle == "20x")[, "F.value"], digits = 2)`, P-value = `r format(filter(mock_anova_summary, sub_sample_level == 1000, cycle == "20x")[, "bh"], digits = 1, nsmall = 1)`) [Table S4]. Using a Tukey post-hoc test, the majority of differences for the number of OTUs detected in the mock community was largely due to Kappa and Platinum versus the other polymerases across the number of cycles used [Table S5]. Similarily, differences in the range of the number of OTUs detected for fecal samples was dependent on the polymerase used (e.g. Accuprime at 35 cycles = `r filter(fecal_numOTU_data, cycles == "35x", taq == "Accuprime") %>% pull(taq_min)` - `r filter(fecal_numOTU_data, cycles == "35x", taq == "Accuprime") %>% pull(taq_max)` versus Phusion at 35 cycles = `r filter(fecal_numOTU_data, cycles == "35x", taq == "Phusion") %>% pull(taq_min)` - `r filter(fecal_numOTU_data, cycles == "35x", taq == "Phusion") %>% pull(taq_max)`) [Figure 3B]. There was also a trend for lower number of cycles (15-20) to result in a reduced range in the number of OTUs versus higher number of cycles (25, 30, and 35) for all polymerases (e.g. Phusion at 15 cycles = `r filter(fecal_numOTU_data, cycles == "15x", taq == "Phusion") %>% pull(taq_min)` - `r filter(fecal_numOTU_data, cycles == "15x", taq == "Phusion") %>% pull(taq_max)` versus Phusion at 35 cycles = `r filter(fecal_numOTU_data, cycles == "35x", taq == "Phusion") %>% pull(taq_min)` - `r filter(fecal_numOTU_data, cycles == "35x", taq == "Phusion") %>% pull(taq_max)`) [Figure 3B]. Unlike mock community samples, an overall difference in the number of OTUs was only detected between polymerases at 35 cycles in fecal samples (F-stat > `r round(min(filter(fs_anova_summary, cycle == "35x", sub_sample_level == 1000)[, "F.value"]), digits = 2)`, P-value = `r format(filter(fs_anova_summary, cycle == "35x", sub_sample_level == 1000)[, "bh"], digits = 2, nsmall = 2, scientific = T)`) [Table S4], and a Tukey post-hoc test failed to identify any differences between specific polymerase groups (P-value `r ifelse(min(filter(fs_tukey_summary, sub_sample_level == 1000)[, "padj"]) > 0.05,  invisible(">"), invisible("check data"))` 0.05) [Table S5]. Overall, mock communities showed a noticeably larger difference between polymerases in the number of OTUs than actual fecal samples [Figure 3 & Table S4-S5]. This was consistent across the number of amplification cycles tested [Figure 3]. Based on these observations, it is clear that larger differences in total number of OTUs based on polymerases are found in mock versus fecal communities.

@@

***Variation due to polymerase and number of cycles is dwarfed by the biological variation of an individual.***
Using 16S rRNA gene sequencing data there was a large disparity in a model's ability to correctly classify samples based on polymerase used, number of cycles, and individual [Figure 5A]. The model classification success for an individual was significantly better than all other models tested [Figure 5A & Table S8]. Additionally, the top 10 most impotant variables to the polymerase and number of cycle models were not the most important variables in the model classifying individuals [Figure 5B]. This observation shows that OTUs that change due to the number of cycles and polymerase used are not the same as OTUs that differentiate between indvidiuals [Figure 5B]. Although there are a variety of errors associated with the amplification process, they are smaller than the bacterial community variation between indviduals.

@@

Previous studies have reported GC dependent amplification differences [@polz_bias_1998] and we confirm that these differences still persist in high fidelity DNA polymerase when analyzing mock community samples [Figure 1]. Additionally, these specific polymerases have different sequence error rates and chimera prevalence [Figure 2]. Chimera prevalence in particular was strongly associated with the total number of OTUs detected in a mock community [Figure 2E]. This total number of OTUs also varied by polymerase used for these mock community samples [Fiugre 3A]. The range in the number of OTUs observed increased with the number of cycles and the change in range was dependent on the polymerase for both mock community and fecal samples [Figure 3]. However, these differences did not translate to large bacterial community composition changes based on polymerase [Figure 4]. Even though there were bacterial community composition changes based on the number of cycles they occured independently of the polymerase used [Figure 4]. Additionally, there were no OTU-based differences observed within the number of cycles between any of the polymerases for fecal samples. When Random Forest models were created to classify number of cycles, polymerase, and individual based on the 16S rRNA gene sequencing, the model performance for individuals was significantly greater than all other models tested [Figure 5A]. In addition to the better model performance of individuals, the most important OTUs to this model were not the most important OTUs for the other models tested [Figure 5B]. Our observations show that differences between high fidelity DNA polymerases can be found. However, when using 16S rRNA gene sequencing these technical differences are dwarfed by biological differences between fecal bacterial communities within individuals.

>>>>

**Conclusions.** Although there are 16S rRNA gene sequencing differences based on polymerase and number of cycles used, they are small with respect to the biological differences between fecal bacterial communities within individuals. Collectively, these results provide evidence that a real biological difference between groups, based on 16S rRNA gene sequencing of fecal samples, should be detectable regardless of polymerase and number of cycles used.

@@

The bacterial community is reported to vary between case and control for a number of diseases [@Turnbaugh2008; @Baxter2016; @Sze2015; @Bonfili2017]. However, for diseases like obesity, the taxa identified have varied widely depending on the study [@Turnbaugh2008; @Zupancic2012]. Some of this variation could be due to error introduced during the 16S rRNA gene sequencing workflow. A typical 16S rRNA gene sequencing workflow can be divided into preservation, extraction, PCR, and sequencing steps. The preservation and extraction stages of the 16S rRNA gene sequencing workflow have been the most extensively studied [@contamination_Salter2014; @preservation_Song_2016; @storage_Bassis_2017; @review_Kim_2017]. For preservation and extraction stages of the workflow, it has been consistently found that there are errors in the observed bacterial community composition based on the kits used, but that these differences are smaller than the overall biological difference measured between samples with different kits [@preservation_Song_2016; @storage_Bassis_2017]. Since these studies use the same PCR approach while varying preservation or extraction method, the contribution of PCR error to this overall workflow is not as well characterized.

There is a large body of literature that shows there are errors due to primer and number of cycles chosen for the PCR stage of 16S rRNA gene sequencing [@Eckert1991; @Burkardt2000]. Primers have variable region dependent binding affinities which causes an inability to detect specific bacteria (e.g. V1-V3 does not detect *Haemophilus influenzae* and V3-V5 does not detect *Propionibacterium acnes*) [@Meisel2016; @Sze2015 (Table S4)]. Another source of error is the selective amplification of AT-rich over GC-rich sequences which exaggerate the difference between 16S rRNA genes higher in AT versus those higher in GC content [@polz_bias_1998]. Many of these sources of error are made worse as the number of cycles increases [@Wang1996; @Haas2011; @Kebschull2015]. For example, both amplification error and non-specific amplification (e.g. incorrect amplicon size products) also can increase as the number of cycles increases. This will increase the number of Operational Taxonomic Units (OTUs) observed and drastically change the values obtained from commonly used diversity measures [@BautistadelosSantos2016; @Acinas2005]. Additionally, as the number of cycles increases more chimeras can form from an aborted extension step that causes a priming error and subsequent secondary extension [@Haas2011]. These chimeras will artificially increase community diversity by increasing the number of OTUs that are observed [@Haas2011]. In addition to these sources of errors, there also are multiple families of DNA polymerases that have their own error rate and proof reading capacity [@polymerase_Ishino_2014]. For simplicity, the use of the term 'error' within the context of this study will be used as a broad term for changes in the downstream sequencing results due to the amplification step (e.g. higher GC content genomes, base substitutions, chimeras, changes from the expected relative abundance, etc.).

Interestingly, the influence different DNA polymerases can have on the observed 16S rRNA gene sequencing results have not been well studied like some of the other sources of PCR-based error. A recent study found differences in the number of OTUS and chimeras between normal and high fidelity DNA polymerases [@taq_Gohl_2016]. The authors of this study could reduce the difference between two polymerases by optimizing the annealing and extension steps within the PCR protocol [@taq_Gohl_2016]. Yet, within this study there was no comparison made between different high fidelity DNA polymerases on the same samples. The authors instead focused their efforts on testing specific types of amplification methods. Additionally, the fecal samples that were analyzed, as a model of a more complex community, may overestimate the biological variation in human samples due to the comparison of captive versus semi-captive red-shanked doucs. Due to these gaps, it makes sense to extend the previous line of inquiry to include a more detailed examination of two specific areas. First, whether differences in PCR error are detected based on number of cycles used and high fidelity polymerases. Second, whether these differences in error are enough to obscure smaller biological signals than what has been previously reported [@taq_Gohl_2016].

This study will investigate whether there are error differences that are dependent on high fidelity DNA polymerases and whether these differences obscure the biological variation in the fecal bacterial communities between individuals. We accomplish this by first examining GC-based amplification error, sequence error (e.g. substitutions), chimera prevalence, the number of OTUs, Bray-Curtis index, and OTU-based differences at varying number of cycles in five different high fidelity DNA polymerases in mock communities. In addition to these metrics we also created Random Forest models of the mock community to assess how successful classification based on 16S rRNA gene sequencing of number of cycles and type of polymerase could be. We then assessed if similar differences in the number of OTUs, Bray-Curtis index, and OTUs could be detected in human fecal samples. Additionally, we also created Random Forest models to assess how successful they could be at classifying fecal samples by number of cycles, polymerase used, or individual. Collectively, our observations suggest that although detectable differences occur based on number of cycles or high fidelity DNA polymerase used, they are smaller than the biological differences between individuals.

@@

***Sequence processing.***
The mothur software program was used for all sequence processing steps [@mothur_schloss_2009]. The protocol has been previously published [@protocol_Kozich_2013] (https://www.mothur.org/wiki/MiSeq_SOP). Two major differences from the published protocol were the use of VSEARCH instead of UCHIME for chimera detection and the use of the OptiClust algorithm instead of average neighbor for OTU generation at 97% similarity [@vsearch_Rognes_2016; @uchime_Edgar_2011; @opticlust_Westcott_2017]. Sequence error was determined using the 'seq.error' command on mock samples to compare back to the reference 16S sequences of *P. aeruginosa*, *E. coli*, *S. enterica*, *L. fermentum*, *E. faecalis*, *S. aureus*, *L. monocytogenes*, and *B. subtilis* [@mothur_schloss_2009; @vsearch_Rognes_2016; @rdp_Cole_2013]. For simplicity, the use of the term 'error' within the context of this study moving forward encompasses changes in the downstream sequencing results due to the amplification step (e.g. higher GC content genomes, base substitutions, deletions, insertions, non-specific amplification, chimeras, etc.).

@@

***Statistical analysis.***
All analysis was done with the R (v `r paste(version$major, ".", version$minor, sep = "")`) software package [@r_citation_2017]. Data transformation and graphing was completed using the tidyverse package (v `r paste(packageVersion("tidyverse")[1])`) and colors selected using the viridis package (v `r paste(packageVersion("viridis")[1])`) [@tidyverse_2017; @viridis_citation_2017]. High and low GC content was determined based on the median GC percentage of either the V4 region or the whole genome of the bacterial species used in the mock community. Differences in the total number of OTUs were analyzed using an ANOVA with a tukey post-hoc test. For the comparison of the number of OTUS in fecal samples the data was normalized to each individual by cycle number to account for the biological variation. Bray-Curtis distance matrices were generated using mothur. The distance matrix data was analyzed using PERMANOVA with the vegan package (v `r paste(packageVersion("vegan")[1])`) [@vegan_citation] and Kruskal-Wallis tests within R. The Random Forest models were run using the caret package (v `r paste(packageVersion("caret")[1])`) [@caret_citation]. A total of 100 10-fold CV runs on different 80/20 splits of the data was run to generate a range of the Logloss value. The probability of a correct call was obtained from this Logloss value by taking the negative natural logarithm. For both error and chimera analysis, samples were tested using Kruskal-Wallis with a Dunns post-hoc test. Where applicable, correction for multiple comparison utilized the Benjamini-Hochberg method [@benjamini_controlling_1995].

@@

***The number of OTUs generated are dependent on polymerase used.***
In addition to the sequence error and chimera differences between polymerases, we also investigated whether there were polymerase or number of cycle dependent effects on the observed number of OTUs. There was a polymerase dependent difference in the range of the number of OTUs in the mock community samples [Figure 3A]. The closest any of the polymerases came to a total of `r pull(ref_mock_otu_num, numOtus)` OTUs, created by running the mock reference 16S sequences through mothur processing, was at 25 and 30 cycles [Figure 3A]. Differences between polymerases for the number of OTUs created were observed as early as 20 cycles in the mock community (F-stat = `r round(filter(mock_anova_summary, sub_sample_level == 1000, cycle == "20x")[, "F.value"], digits = 2)`, P-value = `r format(filter(mock_anova_summary, sub_sample_level == 1000, cycle == "20x")[, "bh"], digits = 1, nsmall = 1)`) [Table S4]. Using a Tukey post-hoc test, the majority of differences for the number of OTUs detected in the mock community was largely due to Kappa and Platinum versus the other polymerases across the number of cycles used [Table S5]. Similarly, differences in the range of the number of OTUs detected for fecal samples was dependent on the polymerase used (e.g. Accuprime at 35 cycles = `r filter(fecal_numOTU_data, cycles == "35x", taq == "Accuprime") %>% pull(taq_min)` - `r filter(fecal_numOTU_data, cycles == "35x", taq == "Accuprime") %>% pull(taq_max)` versus Phusion at 35 cycles = `r filter(fecal_numOTU_data, cycles == "35x", taq == "Phusion") %>% pull(taq_min)` - `r filter(fecal_numOTU_data, cycles == "35x", taq == "Phusion") %>% pull(taq_max)`) [Figure 3B]. There was also a trend for lower number of cycles (15-20) to result in a reduced range in the number of OTUs versus higher number of cycles (25, 30, and 35) for all polymerases (e.g. Phusion at 15 cycles = `r filter(fecal_numOTU_data, cycles == "15x", taq == "Phusion") %>% pull(taq_min)` - `r filter(fecal_numOTU_data, cycles == "15x", taq == "Phusion") %>% pull(taq_max)` versus Phusion at 35 cycles = `r filter(fecal_numOTU_data, cycles == "35x", taq == "Phusion") %>% pull(taq_min)` - `r filter(fecal_numOTU_data, cycles == "35x", taq == "Phusion") %>% pull(taq_max)`) [Figure 3B]. Unlike mock community samples, an overall difference in the number of OTUs was only detected between polymerases at 35 cycles in fecal samples (F-stat > `r round(min(filter(fs_anova_summary, cycle == "35x", sub_sample_level == 1000)[, "F.value"]), digits = 2)`, P-value = `r format(filter(fs_anova_summary, cycle == "35x", sub_sample_level == 1000)[, "bh"], digits = 2, nsmall = 2, scientific = T)`) [Table S4], and a Tukey post-hoc test failed to identify any differences between specific polymerase groups (P-value `r ifelse(min(filter(fs_tukey_summary, sub_sample_level == 1000)[, "padj"]) > 0.05,  invisible(">"), invisible("check data"))` 0.05) [Table S5]. Overall, mock communities showed a noticeably larger difference between polymerases in the number of OTUs than actual fecal samples [Figure 3 & Table S4-S5]. This was consistent across the number of amplification cycles tested [Figure 3]. Based on these observations, it is clear that larger differences in total number of OTUs based on polymerases are found in mock versus fecal communities.

@@

***Variation due to polymerase and number of cycles is dwarfed by the biological variation of an individual.***
Using 16S rRNA gene sequencing data there was a large disparity in a model's ability to correctly classify samples based on polymerase used, number of cycles, and individual [Figure 5A]. The model classification success for an individual was significantly better than all other models tested [Figure 5A & Table S8]. Additionally, the top 10 most important variables to the polymerase and number of cycle models were not the most important variables in the model classifying individuals [Figure 5B]. This observation shows that OTUs that change due to the number of cycles and polymerase used are not the same as OTUs that differentiate between individuals [Figure 5B]. Although there are a variety of errors associated with the amplification process, they are smaller than the bacterial community variation between individuals.

@@

Previous studies have reported GC dependent amplification differences [@polz_bias_1998] and we confirm that these differences still persist in high fidelity DNA polymerase when analyzing mock community samples [Figure 1]. Additionally, these specific polymerases have different sequence error rates and chimera prevalence [Figure 2]. Chimera prevalence in particular was strongly associated with the total number of OTUs detected in a mock community [Figure 2E]. This total number of OTUs also varied by polymerase used for these mock community samples [Figure 3A]. The range in the number of OTUs observed increased with the number of cycles and the change in range was dependent on the polymerase for both mock community and fecal samples [Figure 3]. However, these differences did not translate to large bacterial community composition changes based on polymerase [Figure 4]. Even though there were bacterial community composition changes based on the number of cycles they occurred independently of the polymerase used [Figure 4]. Additionally, there were no OTU-based differences observed within the number of cycles between any of the polymerases for fecal samples. When Random Forest models were created to classify number of cycles, polymerase, and individual based on the 16S rRNA gene sequencing, the model performance for individuals was significantly greater than all other models tested [Figure 5A]. In addition to the better model performance of individuals, the most important OTUs to this model were not the most important OTUs for the other models tested [Figure 5B]. Our observations show that differences between high fidelity DNA polymerases can be found. However, when using 16S rRNA gene sequencing these technical differences are dwarfed by biological differences between fecal bacterial communities within individuals.
